%-------------------------
% Resume in Latex
% Author : Anurag Tripathi
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Anurag Tripathi} & Email : \href{mailto:tanurag640@gmail.com}{tanurag640@gmail.com}\\
   & Mobile : +91-9538346822 \\
\end{tabular*}

\vspace*{10px}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
   \resumeSubheading
      {CDAC}{Bengalure,KA}
      {PG Diploma in System Software Design }{Aug. 2008 -- July. 2012}
    \resumeSubheading
      {UPTU}{Lucknow,UP}
      {B.Tech In Information Technology}{Jul 2009 -- June 2013}
  \resumeSubHeadingListEnd

\vspace*{10px}

%-----------EXPERIENCE-----------------
\section{Experience}
\vspace*{5px} 
  \resumeSubHeadingListStart

    \resumeSubheading
      {Western Digital}{Bengaluru}
      {Senior Engineer,Firmware Engineering}{March 2016 - Present}
      \resumeItemListStart
        \resumeItem{Oakgate NVME FrameWork}
          {API's and framework written in C/C++ on top of Oakgate API's to write test cases for NVME Protocol Compliance Testing.}
        \resumeItem{Auto Test Executer}
          {A GUI Written in C++ to execute protocol compliance testing with automatic report generation , different timing reports , eg:command execution times,test report generation, automatic scheduling of of tests on multiple platforms.}
        \resumeItem{Switcher}
        {A python library and Tkinter GUI  to switch between multiple devices connected to the Switcher Hardware }
        \resumeItem{Lecroy PCIe Compliance}
        {PCIe Phy Layer/Link Layer/Transport Layer Error Injection Scripts to test NVME Compliance.}
      \resumeItemListEnd
      \vspace*{5px} 
    \resumeSubheading
      {Tech Mahindra}{Bengaluru}
      {Engineer}{Jun 2014 - Mar 2016}
      \resumeItemListStart
        \resumeItem{On Tap Updation}
          {Client NetApp: NetApp's storage fillers ontap software updation}
        \resumeItem{Portable Traffic Lights}
          {Developed Pseudo SPI Framework on top of PRU unit to communicate between different modules.}
        \resumeItem{NVME Test Framework}
          {Test Framework for doing NVME Compliance Testing. Added python layer on top of C/C++ API's using boost python.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace*{10px} 
%-----------SKILLS-----------------%/
\section{Skills}
\vspace*{5px} 
      \resumeSubHeadingListStart
        \resumeSubItem{Languages}{: C,C++,Python}
        \resumeSubItem{Technologies}{: Linux Device Drivers,Linux System Software,Windows System Software}
        \resumeSubItem{Tools}{: gdb,eclipse,git,svn,visual Studio,Vim}
        \resumeSubItem{Protocols}{: NVME,SATA,SPI,CAN,UART,USB}
        \resumeSubItem{Platforms}{: Beaglebone,STM32,Arduino}
      \resumeSubHeadingListEnd
\vspace*{10px} 
%-----------PROJECTS-----------------
\section{Projects}
\vspace*{5px} 
  \resumeSubHeadingListStart
    \resumeSubItem{ATA Passthrogh}
      {Layer written in python to send SATA Command to connected device using Windows IOCTL }
    \resumeSubItem{Embedded Firewall}
      {Embedded Firewall using beaglebone and linux netfilter framework.}
    \resumeSubItem{USB Driver}
      {Linux USB Data Collection device driver.}
    \resumeSubItem{UART Linux Driver}
      {Custom Linux device driver for UART}
    \resumeSubItem{OpenStack Setup}
      {POC on Openstack Cloud Setup , Chef Setup}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
